Collocated Snapshot Backup with VM-Centric Deduplication in the Cloud

### 2013-09-24 snapshot_system/fast14_evaluation.tex
update

Figure~\ref{fig:exbin-efficiency-graph2} also shows the effectiveness of the local similarity-based search in VC.
Without this (i.e. when we only check the parent segment at the same offset), when an entire
segment is moved to another location on disk, for example when a file is rewritten
rather than modified in place, the deduplication opportunity is missed. We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently,
so the similarity search becomes important for those VMs.
In general, our experiments show that
dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
which leads about 75.86\% reduction.
Similarity-guided local search can further reduce the data size
to about 12.05\% of original size, namely it delivers additional 12.09\% reduction.
The PDS-based cross-VM detection with $\sigma=2\% $
can reduce the size further to 8.6\% of original size, namely it 
delivers additional 3.45\% reduction.

>>>>

Figure~\ref{fig:exbin-efficiency-graph2} also shows the effectiveness of the local similarity-based search in VC.
Without this (i.e. when we only check the parent segment at the same offset), when an entire
segment is moved to another location on disk, for example when a file is rewritten
rather than modified in place, the deduplication opportunity is missed. We have found that in
approximately 1/3 of the VMs in our dataset this movement happens frequently,
so the similarity search becomes important for those VMs.
% In general, our experiments show that
% dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
% which leads about 75.86\% reduction.
% Similarity-guided local search can further reduce the data size
% to about 12.05\% of original size, namely it delivers additional 12.09\% reduction.
% The PDS-based cross-VM detection with $\sigma=2\% $
% can reduce the size further to 8.6\% of original size, namely it 
% delivers additional 3.45\% reduction.
In general, our experiments show that
dirty-bit detection at the segment level can reduce the data size to about 24.14\% of original data, 
which leads to about 75.86\% reduction.
Similarity-guided local search can further reduce the data size
to about 12.05\% of original, namely it delivers 50.08\% reduction to the dirty segments.
The popularity-guided global deduplication with $\sigma=2\% $
can reduce the data further to 8.6\% of its original size, 
it provides additional 28.63\% reduction to the remaining data.
